### 2013-08-13 Tex/chapters/results.tex
Weitere Verbesserungen der Form

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N} H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{sssec:eqtime}). The used values for different system sizes
are listed in tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
the \(t_{eq}\) values are generously rounded up to be on the safe side
and the \(\tau\) values are determined as the maximum \(\tau\) over all
simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
and rounded up to the next integer.
\begin{table}[htbp]
    \center
    \begin{tabular}{l r r r r r}
        \toprule
        \(L\)    & 16 &  32 &  64 & 128 & 256\\
        \midrule
        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
        \bottomrule
    \end{tabular}
    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
    \label{tab:tauAndTeq}
\end{table}\\
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
calculated sweeps totals to
\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
The expected values \(\avg{O}\) for \(100\) different random proximity
graphs with the same disorder parameter \(\sigma\) are then averaged to
\(\overline{\avg{O}}\). Not only the seed to generate the new random
realization of the proximity graph gets changed, but also the seed for
the random numbers used in the Monte Carlo simulation and during the
generation of the random start configuration of the spins.\\
The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
\cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
\(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
over different realizations of the random proximity graph, which are
surely uncorrelated.
Because every error mentioned in this thesis is of this type, it is not
necessary to determine \(\tau\) for each observable. Therefore a good
error estimate can be achieved by simple bootstrapping. Though one has
to simulate enough uncorrelated states for each realization, to keep
the \(\Delta \overline{\avg{O}}\) small. For every determined value an
error is calculated and given in the form \texttt{value(error of last digit)}.
The error given for fits are the asymptotic standard errors as calculated
by gnuplot\footnote{An open source plotting program, used for all plots and fits in this thesis. \url{http://gnuplot.info/}.}.

@@

        \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
        {
            Top: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the RNG and
            \subref{sfig:sumJ:GG} the GG.\\
            Bottom: Critical temperatures normalized by mean sum of the
            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
            disorder parameters for
            \subref{sfig:Tc_normJ:RNG} the RNG and
            \subref{sfig:Tc_normJ:GG} the GG.
        }
        \label{fig:TcJ}
    \end{figure}\\
    Though eq. \eqref{eq:exactHCTc} shows, that there does not have
    to be a linear connection between \(J\) and \(T_c\), the best guess
    is a linear connection, because this model is derived from the
    square lattice, where the connection is linear. Therefore, one
    normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
    \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
    jump on the GG arises again, but \(T_c\) is now monotonically
    decreasing with increasing disorder parameter \(\sigma\).
    %~ This is a strong hint, that the change of the \(T_c\) with changing
    %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
    %~ expected conclusion.\\
    Moreover the forms of both curves are quite similar, but the
    one for the RNG \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the GG \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
    disorder has little influence on this normalized critical temperature.
    Also both graph types have a steep decline after the plateau before
    they approach an asymptotic limit for \(\sigma \gg 1\)\\\\

>>>>

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N} H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{sssec:eqtime}). The used values for different system sizes
are listed in tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
the \(t_{eq}\) values are generously rounded up to be on the safe side
and the \(\tau\) values are determined as the maximum \(\tau\) over all
simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
and rounded up to the next integer.
\begin{table}[htbp]
    \center
    \begin{tabular}{l r r r r r}
        \toprule
        \(L\)    & 16 &  32 &  64 & 128 & 256\\
        \midrule
        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
        \bottomrule
    \end{tabular}
    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
    \label{tab:tauAndTeq}
\end{table}\\
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
calculated sweeps totals to
\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
The expected values \(\avg{O}\) for \(100\) different random proximity
graphs with the same disorder parameter \(\sigma\) are then averaged to
\(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
are omitted in the following for the sake of simplicity.\\
Not only the seed to generate the new random
realization of the proximity graph gets changed, but also the seed for
the random numbers used in the Monte Carlo simulation and during the
generation of the random start configuration of the spins.\\
The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
\cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
\(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
over different realizations of the random proximity graph, which are
surely uncorrelated.
Because every error mentioned in this thesis is of this type, it is not
necessary to determine \(\tau\) for each observable. Therefore a good
error estimate can be achieved by simple bootstrapping. Though one has
to simulate enough uncorrelated states for each realization, to keep
the \(\Delta \overline{\avg{O}}\) small. For every determined value an
error is calculated and given in the form \texttt{value(error of last digit)}.
The error given for fits are the asymptotic standard errors as calculated
by gnuplot. Gnuplot is an open source plotting program, used for all plots
and fits in this thesis \footnote{\url{http://gnuplot.info/}.}.

@@

        \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
        {
            Top: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the RNG and
            \subref{sfig:sumJ:GG} the GG.\\
            Bottom: Critical temperatures normalized by mean sum of the
            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
            disorder parameters for
            \subref{sfig:Tc_normJ:RNG} the RNG and
            \subref{sfig:Tc_normJ:GG} the GG.
        }
        \label{fig:TcJ}
    \end{figure}\\
    Though eq. \eqref{eq:exactHCTc} shows, that there does not have
    to be a linear connection between \(J\) and \(T_c\), the best guess
    is a linear connection, because this model is derived from the
    square lattice, where the connection is linear. Therefore, one
    normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
    fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
    jump on the GG arises again, but \(T_c\) is now monotonically
    decreasing with increasing disorder parameter \(\sigma\).
    %~ This is a strong hint, that the change of the \(T_c\) with changing
    %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
    %~ expected conclusion.\\
    Moreover the forms of both curves are quite similar, but the
    one for the RNG in fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the GG in fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
    disorder has little influence on this normalized critical temperature.
    Also both graph types have a steep decline after the plateau before
    they approach an asymptotic limit for \(\sigma \gg 1\)\\\\
